Adaptive Scheduling of Scientific Workflows

### 2024-03-21 main.tex
temp new heuristic

@@

>>>>

\newcommand{\MM}{M}
\newcommand{\MC}{MC}
\newcommand{\rt}{rt}
\newcommand{\curM}{curM}
\newcommand{\curC}{curC}
\newcommand{\PD}{PD}

@@

\section{Proposal of a new heuristic with slightly refined model}

The idea is to get rid of the constraint that a processor handles a {\em block} of tasks,
but favor processor reuse as is done in HEFT.

\subsection{Model}

For a task~$u\in V$, we have a memory usage~$m_u$ and execution time~$w_u$.
For an  edge $(u,v)\in E$, we have a data of size $c_{u,v}$.

For each processor $P_j$, we have a speed~$s_j$, and also two memory bounds: 
$\MM_j$ the processor memory, and $\MC_j$, the size of the communication buffer.
We can decide to evict some data from the main memory if we are sending the data
to another processor; it then stays in the communication buffer until it has been sent.

We keep track of the current ready time of each processor and each communication
channel, $\rt_j$ and $\rt_{j,j'}$, for all processors~$(j,j')$. Initially, all the ready times
are set to~$0$.

We also keep track of the current memory usage, $\curM_j$ and $\curC_j$,
on respectively the processor memory and communication buffer. 
Furthermore, $\PD_j$ is a priority queue with the {\em pending data} 
that are in $\MM_j$ but may be evicted to be communicated, if 
more memory is needed on~$p_j$. They are ordered by non-decreasing size. 
They correspond to some $c_{u,v}$'s.

\subsection{Heuristics}

We consider two variants of HEFT accounting for memory usage, which only
differ in the order they consider tasks to be scheduled.

HEFTM-BL orders tasks by non-increasing bottom levels, where the bottom
level is defined as
$$bl(u) = w_u + \max_{(u,v)\in E} \{c_{u,v} + bl(v)\}$$
 (the max is 0 if there is no outgoing edge).

HEFTM-MM orders tasks as dictated by MinMem.
\AB{Actually, while writing,
I remember that this might be complicated to compute MinMem for the
entire graph, so this might not be a feasible variant, or needs to be updated?}

Then, the idea is to pick the next free task in the given order,
and greedily assign it to a processor, by trying all possible options
and keeping the most promising one.

\medskip
\noindent{\em Tentative assignment of task~$v$ on $p_j$.}\\
{\bf Step 1.} First, we need to check that for all predecessors~$u$ of~$v$ that are mapped
on~$p_j$, the data $c_{u,v}$ is still in the memory of~$p_j$, 
i.e., $c_{u,v}\in PD_j$. Otherwise, the finish time is set to~$+\infty$ (invalid choice).

\smallskip
\noindent{\bf Step 2.} Next, we check the memory constraint on~$p_j$, by computing
$$Res = \curM_j  + m_v + \sum_{u \in Pred(v), u\notin T(p_j)}  \{c_{u,v}\}
+ \sum_{w\in Succ(v)}  \{c_{v,w}\} - \MM_j .$$

$T(p_j)$ is the set of tasks already scheduled on $p_j$; by step 1, their files are
already in the memory of~$p_j$. However, the files from the 
other predecessor tasks must be loaded in memory before executing task~$v$,
as well as $m_v$ and the data generated for all successor tasks.
$Res$ is then checking whether there was enough memory; if it is positive, 
it means that we have exceeded the memory of~$p_j$ with this tentative 
assignment.

In this case ($Res >0$), we  try evicting
some data from memory so that we have enough memory to execute task~$v$. 
We need to evict at least $Res$ data. For now, we propose a greedy approach,
evicting the largest files of $\PD_j$ until $Res$ data has been evicted. 
\AB{I can further detail if needed, moving data of $\PD_j$ from $\curM_j$
to $\curC_j$, and removing it from $\PD_j$...}
If we still do not have enough memory after having tentatively evicted all files from $\PD_j$,
we set the finish time to~$+\infty$ (invalid choice).

\smallskip
\noindent{\bf Step 3.} We tentatively assign task~$v$ on $p_j$. Its starting time $st_v$
is dictated by the maximum between $rt_j$, and all communications that
must be orchestrated from predecessor tasks $u\notin T(p_j)$. Its
finish time on $p_j$ is then 
$FT(v,p_j) = st_v + \frac{w_v}{s_j}$.

\medskip
\noindent{\em Assignment of task~$v$.}\\
Once we have computed all finish times for task~$v$, 
we keep the minimum $FT(v,p_j)$ and assign task~$v$
to processor~$p_j$, updating $\MM_j$ and $\MC_j$ as needed,
as well as all the $rt$ values for $p_j$ and the communication channels.

\section{Conclusion}
